Understanding Expectation Formation from Probabilistic Surveys

### 2019-06-17 slides/ExpSlides.tex
generated graphs and aregressions for quarterly data
Updating slides including IR plots
Include IR plots without mp shocks

\documentclass{beamer}
\usepackage{default}
\usepackage{amsmath}
\usepackage{graphicx}

@@

\begin{frame}{Population moments: disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_diag.png} 
\end{figure}
\end{frame}

@@

\begin{frame}{Population moments: uncertainty and disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/var_diag.png} 
\end{figure}
\end{frame}

@@

@@

\begin{itemize}
	\item \textbf{Measurement Errors}:  winsorization is still necessary
	\item \textbf{Density Estimation}: generalized beta estimation, \cite{engelberg2009comparing}
    \item \textbf{Identification of Shocks}: following \cite{coibion2012can}
\end{itemize}

>>>>

\documentclass{beamer}
\usepackage{default}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{adjustbox}  % Allows for fitting tables into slide

@@

\begin{frame}{Population moments: average uncertainty}
\begin{figure}
	\includegraphics[scale=0.3]{figures/var_var.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_disg.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/mean_disg.png} 
\end{figure}
\end{frame}

@@

\begin{frame}{Population moments: uncertainty and disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/var_disg.png} 
\end{figure}
\end{frame}

\begin{frame}{Population moments: uncertainty and disagreements}
\begin{figure}
	\includegraphics[scale=0.3]{figures/var_disg2.png} 
\end{figure}
\end{frame}

@@

\section{Empirical Results}

@@

\begin{itemize}

\item \textbf{Density Estimation}: generalized beta estimation, \cite{engelberg2009comparing}
 \item \textbf{Identification of Shocks}: following \cite{coibion2012can} and monetary policy shocks. 
\end{itemize}

\subsection{Test of Null Hypothesis of Rational Expectation}

\begin{frame}{Test of Rational Expectation}
\begin{table}[tbhp] \centering \adjustbox{max height=\dimexpr\textheight-5.5cm\relax, max width=\textwidth}{
	\begin{tabular}{lllllll}
		\hline 
		& SPFCPI\_FElvl       & SPFPCE\_FElvl & SPFCPI\_Vardiff & SPFPCE\_Vardiff & SPFCPI\_Disgdiff & SPFPCE\_Disgdiff            \\
		\hline 
		L.InfExp\_FE        & 0.941***      & 1.195***        &                 &                  &                  &           \\
		& (0.0840)      & (0.142)         &                 &                  &                  &           \\
		L2.InfExp\_FE       & -0.313**      & -0.625**        &                 &                  &                  &           \\
		& (0.116)       & (0.198)         &                 &                  &                  &           \\
		L3.InfExp\_FE       & 0.114         & 0.0782          &                 &                  &                  &           \\
		& (0.114)       & (0.196)         &                 &                  &                  &           \\
		L4.InfExp\_FE       & -0.137        & -0.0162         &                 &                  &                  &           \\
		& (0.0820)      & (0.131)         &                 &                  &                  &           \\
		L.InfExp\_Var\_ch   &               &                 & -0.855***       & -0.565**         &                  &           \\
		&               &                 & (0.189)         & (0.162)          &                  &           \\
		L2.InfExp\_Var\_ch  &               &                 & -0.780**        & -0.452*          &                  &           \\
		&               &                 & (0.220)         & (0.186)          &                  &           \\
		L3.InfExp\_Var\_ch  &               &                 & -0.556*         & -0.429*          &                  &           \\
		&               &                 & (0.219)         & (0.189)          &                  &           \\
		L4.InfExp\_Var\_ch  &               &                 & -0.167          & 0.00385          &                  &           \\
		&               &                 & (0.188)         & (0.172)          &                  &           \\
		L.InfExp\_Disg\_ch  &               &                 &                 &                  & -0.571***        & -0.640*** \\
		&               &                 &                 &                  & (0.0699)         & (0.127)   \\
		L2.InfExp\_Disg\_ch &               &                 &                 &                  & -0.376***        & -0.0944   \\
		&               &                 &                 &                  & (0.0764)         & (0.141)   \\
		L3.InfExp\_Disg\_ch &               &                 &                 &                  & -0.0455          & 0.180     \\
		&               &                 &                 &                  & (0.0661)         & (0.138)   \\
		L4.InfExp\_Disg\_ch &               &                 &                 &                  & -0.110*          & -0.0364   \\
		&               &                 &                 &                  & (0.0479)         & (0.123)   \\
		\hline 
		N                   & 143           & 41              & 44              & 44               & 146              & 44        \\
		R-sq                & 0.593         & 0.750           & 0.384           & 0.322            & 0.356            & 0.496    \\
		\hline 
	\end{tabular}
}
\end{table}
\end{frame}

\begin{frame}{Identified Inflation shocks}

\begin{figure}
	\includegraphics[scale=0.3]{figures/inf_shocksQ.png} 
\end{figure}

\begin{frame}{Results from \cite{coibion2012can}}

\begin{figure}
	\includegraphics[scale=0.3]{figures/RigidityJPEFigure2.png} 
\end{figure}

\begin{frame}{Inflation IR to  shocks}

\begin{figure}
	\includegraphics[scale=0.3]{figures/CPIAU_ashocks.png} 
\end{figure}

\begin{frame}{Inflation IR to  shocks}

\begin{figure}
	\includegraphics[scale=0.3]{figures/PCEPI_ashocks.png} 
\end{figure}

\subsection{Professional forecasters as a baseline }

\begin{frame}{Forecasting errors IR to  shocks}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFFE_ashocks.png} 
\end{figure}

\begin{frame}{Disagreements IR to  shocks}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFDisg_ashocks.png} 
\end{figure}

\begin{frame}{Uncertainty IR to shocks}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFVar_ashocks.png} 
\end{figure}
